\documentclass[11pt]{book}

\newenvironment{code}{\fontfamily{pcr}\selectfont}{\par}

\usepackage{afterpage}
\usepackage{tikz}
\usetikzlibrary{calc}

\title{Easy}
\author{Jason R. Dunavin, F.S.A., M.A.A.A.}

\begin{document}
	\maketitle
	\topskip0pt
	
	``You are … Mr. Markson? Ah, yes – your payment is in order. We understand you come for a LEMP." In his thick Russian accent, it sounded like he said \textit{leemp}. It was a weird thing to come to an abandoned warehouse to discuss with a Russian gangster, this big electrical contraption. But maybe not the weirdest.
	
	``Yes."
	
	``You… understand what that means?"
	
	``Scientifically speaking, I know what a LEMP is – let’s just put it that way."
	
	``You are aware, then, that you won’t be able to fully participate in soc-"
	
	``Aware of it, yes." \textit{Understand it? I'll let you know when I get out West.} Aidan had handed over his phone at the desk so it wouldn't get fried, but then frying it would probably be the best outcome, since the SIM-3 card would give his location away.
	
	\vspace{0.5cm}
	\hrule
	\vspace{0.5cm}
	
	We all begin the same way – blind, screaming, and coated in goop. Aiden Daniel Markson began the traditional way on the morning of March 23, 2032. Aiden's first experience of the world he had entered against his will was a chilly draft, followed by random shouting, a chuckle here and there, some sobbing. A decent enough chap came along to wash the goop off, and then he felt himself floating into the comforting arms (or something or other) of some other thing with a  soft voice and a nice smell to it; in fact, it smelled something like the warm viscera he was only moments earlier surrounded by. Aiden started to drift off to sleep after this welcome development, but his reverie was interrupted by a sharp pinprick.
	
	\afterpage{%
	\vspace*{\fill}

		\begin{tikzpicture}[remember picture, overlay]
			\draw[line width = 1pt] ($(current page.north west) + (1in,-1in)$) rectangle ($(current page.south east) + (-1in,1in)$);
		\end{tikzpicture}
		
		\begin{code}	
			\begin{tabbing}
				0001 \= HIXBOT ADP8144139812-000007C0 \\
				SEARCHING FOR CMS PATIENT CLOUD... DONE \\
				... \\
				0007 \> PROTOCOL INITIATED \\
				0008 \> CHECKING SHIBBOLETH ... DONE \\
				0009 \> PATIENT:  MARKSON, AIDEN DANIEL \\
				0010 \> DOB: 48296.6509606481 \\
				0011 \> STATUS UPDATE ID=0085746212857132 \\
				STATUS UPDATE 0085746212857132 IN PROGRESS ... \\
				0012 \> INTAKE: KCAL=400, NA=1.31 \\
				... \\
				0172 \> na\textunderscore accum = na\textunderscore accum + this.na \\
				0173 \> msg -> "WARNING SODIUM INTAKE EXCEEDS THRESHOLD (days=91)" \\
				0174 \> this.Patient.BP = reportBF(BP); echo "BP 131/85" \\
				... \\
				1378 \> switch \{ \\
				1379 \> case ((sys > 120) \&\& (diast > 80) \&\& (na\textunderscore accum > 2.91)) \\
				1380 \> this.Patient.prem = this.Patient.prem + \\ surchargeSched.diagCode("I10") \\
					 \> ...
				1381 \} \\
				1382 \> msg -> "STG1 HYPERTENSION NOT MANAGED... \\
					 \> SHARED RESPONSIBILITY PAYMENT APPLIED" \\
				CHECKING EMPLOYMENT RECORDS...
			\end{tabbing}
		\end{code}

	\vspace*{\fill}
	\clearpage
	}
	
	Twenty-eight years later, a much larger and goop-free Aiden Daniel Markson plopped down into a dingy hard plastic booth in a downtown Vietnamese noodle shop. He glanced at the menu, and then stared vacantly past the backwards  ``B" in the window (the grade from the city health department – HIGH SODIUM CONTENT – SHARED RESPONSIBILITY PAYMENTS POSSIBLE and ETHNIC/CULTURAL EXEMPTION being the apparent reasons) at the condensation on the window and the lights of the endless city beyond. The shuffling of feet behind him jerked him back into reality.
	
	``You ready to order?" The waitress managed to combine the alertness of a pen poised over a pad and the worldly disinterest of a Finnish graduate student in architecture into a single set of body language without any effort.
	
	``Oh. Yeah. Pho – veggie – spicy. Water to drink. Thanks."
	
	The order was dutifully recorded and remanded to the kitchen without further comment. Minutes later, a steaming bowl arrived along with a glass of iced water. Aidan took a spoonful from the bowl. The warmth of the spicy broth radiated inward, along with no small measure of disappointment. What he really wanted was the beef. He knew, though, that salty beef would totally jack with his biometrics, and he couldn't afford the surcharges for the fat and cholesterol on top of all the sodium. Also, beef - when you could find it - was terribly expensive. The fresh vegetables were an extravagance enough in the city, where there was barely any (non-GMO) green to begin with and the sun didn't shine down here anyhow. 
	
	The best way to eat pho is as follows: just as you're about to cram a chopstick-load of noodles or vegetable matter or whatever into your face, form a sort of channel with your tongue that you prefill with spit as a protective film against the scalding-hot water, which only compounds with the spicy burn. This Aiden did, sending another comforting wave of warmth through his body. Aiden guessed that it wouldn't feel so good when the Medicare nanobots in his blood stream had their say at the first of the month, but this was a comfort food kind of a night. No textured-soy-protein and tunnel-mushroom medley was going to cut it.
	
	The heat having faded from the bowl, Aiden slurped down the rest of the delicious broth, put the bill of \$51.78 on his card, and hit the streets. An extravagance indeed, but being one of Uncle Sam’s spreadsheet jockeys had its perks. Discounts on the train, a One in a newer housing block that he only had to share with one person (a frequently-stoned freelance writer/Uber driver/data scientist contractor named Chandler), an hour-an-a-half train ride from the office.
	
	Aidan put in his earbuds and waded out into the city's mass of humanity. Everybody either was coming home or going to their second (or third) gig. Aiden worked for the good old U. S. of A. and thus was really lucky. At least that’s what he told himself -- one of Uncle Sam’s many complex and sometimes contradictory rules, for regulars like Aiden and sometimes even for the contractors, was that thou shalt have no other employer before him. Loyalty to the cause was big with Uncle Sam. That really sucked -- some contract gigs might help pay down that massive student debt sometime before he died; it might also get him out of the apartment and in with a new crowd. He was sick to death of hearing Chandler ``ideate" out loud through another gadget review. On the other hand, this job paid for more room in this city than most people knew and an occasional shot of moderately fresh vegetables that were grown in actual, relatively unpolluted dirt. It also paid a healthy share of the Medicare premium; still not an easy feat, but others had it worse. There was a family of seven holed up in a Two on his wing because Mom had type II diabetes.
	
	Aiden soothed this bitterness by thumbing up a selection of music on his phone. He tapped the line called ``CHILL" in the music app and streaming into his earbuds was a selection of ambient, arrhythmic music that kind of went with the city around him, all over the place with no discernible beat whatsoever, but with a cool counterpoint to the chaos surrounding him. Brightly-lit ads everywhere; all the major corporations covered. People stomping off to work, hawkers selling things from small electronics to drugs to street food made from God knows what, a few sorry-looking souls standing around a trashcan fire; occasionally, a Government poster ad showing people of multiple ethnicities exercising together, and saying I WANT YOU TO SHARE THE RESPONSIBILITY - PUBLIC HEALTH MATTERS! 
	
	The music's only-partially soothing influence was promptly interrupted by two sharp dings, a couple of seconds apart. Text messages. \textit{Crap}.
	
	\vspace{0.5cm}
	
	\texttt{Chandler: dude wndrng if youd read pc about samsung quasar iv b4 submit, dat thangs DANK} 
	
	\texttt{Brannen Tragen: I need you to come back to the office ASAP.}
	
	\vspace{0.5cm}
	
	Aiden stopped and out fell a heavy sigh. He looked up toward the dark, overcast sky (not that a person could tell day or night from street level, but it was also raining). He was about 30 yards from the train station that would have conveyed him back to his moderately lumpy bed and the loving embrace of Chandler and his editors. He would instead use that train station to schlepp back to the office for what could not possibly be anything good.
	
	\vspace{0.5cm}
	\hrule
	\vspace{0.5cm}
	
	\textit{Out West.} Aiden's last two words to the Russian sparked a memory from college, specifically from one of the humanities courses he had been mandated to take -- Early Film History. He thought he remembered the TA saying that there was supposed to be some kind of romanticism embedded in this phrase, some sense of adventure combined with the thrill of anticipation. That was a hundred and fifty freaking years ago. No romanticism to be had here - All Aiden could feel staring back at the copper coils was a sense of creeping dread.
	
	Four hundred fifty million people in the United States -- ten billion people worldwide -- have to eat. They each also have to occupy a certain volume of the three physical dimensions of space, of which Planet Earth has only a finite livable supply. Balancing these competing goals, it turned out, required optimizing these two quantities.
	
	And optimizing these two quantities, it turned out, required that national governments make people live tightly-packed in cities and cordoning off entire swaths of large interior provinces (the arable ones, anyway) to use as farmland. Government departments or large corporate contractors manage it, and -- \textit{voila!} -- staple crops for everybody. Well, not exactly everybody. But most people. Most people who can work, anyway.
	
	Somebody has to work for these entities. Fewer people /textit{want} to work for them than \textit{have} to work for them. The thirteen million people in the prison populations -- the less violent ones, at least -- provide a source for workers. Immigration -- both legal and illegal -- provide another source. Ten billion people can eat a hell of a lot of food, though, and so more farm workers are needed from somewhere. These are made up of refugees from the contract economy, those who won't -- or can't -- support themselves or their families in the cities. Life is hard for these people, working 12-hour shifts to meet production and shipping targets in support of international treaties on food distribution. The Philippines didn't meet its targets in 2051. The Filipino government -- well, a different Filipino government -- did miraculously meet them in 2052, when three Chinese navy task forces showed up on Filipino patrol scans approaching Manila Bay.
	
	So, yeah, the targets are important. Workers who don't help meet those agricultural targets, can't function in the urban gig economy, and don't have (or can't get) full-spectrum jobs can expect to live what relatively short time is left of their lives in squalor in stacks of shipping containers in some Midwestern shanty town that would offend any Rio de Janeiro street urchin back in Grandpa's day.
	
	Another aspect of this importance is that Uncle Sam and the factory farms offered inducements to subject oneself to this lifestyle - like the forgiveness of part or all of one's student loan debt. More than a few people had to fall back on this carrot in order to spare one's relatives (Uncle Sam had gotten quite a bit more aggressive about recouping its ``investments" during Aidan's lifetime) the stick of several hundred thousand dollars of debt.
	
	Many conglomerates offered another perk, by not really caring too much about meeting employer "public health" targets. Not that they were really pioneers in the employee health space; they didn't much care about actual employee health, either. Employee health targets were important, too -- Uncle Sam liked to lead by example in this regard. Maintaining public health replaced the military draft sometime in the Thirties as the bellwether of public responsibility, and employers went to great lengths to make sure they were hitting their regulatory targets, especially if they wanted something from Uncle Sam. The farm conglomerates' lobbyists had won the freedom to overlook these targets in the name of keeping (most) people fed and thus not rioting constantly. They provided the bare minimum of health care to keep you showing up to work every day, but life expectancy for farm workers was a full six years shorter than for city workers. 
	
	But they didn't check the nanobots. Hell, the farms even took people who got them zapped. Tampering with them was a criminal offense -- Federal property and all that -- thus, the Russian and his clever gangster engineering arrayed before Aiden now. Aiden had made contact through Chandler's marijuana dealer, a friend-of-a-friend thing (maybe ``friend" was the wrong word, but you get the idea). This little 50-millisecond EMP burst had cost him five thousand dollars, which was coming out of his future pay at ADM Monsanto Bayer. Really, they were quite understanding about the money, for a Russian gang. 
	
	There were other consequences too -- who knows what would happen in 45 years when he got eligible for Medicare, assuming such a thing still existed then, and there were no nanobots to monitor or verify his citizenship. Or, if he got into any kind of scrape with the law. Maybe if he wanted to vote in an election at some point (ha!) or travel outside the country (again, not really a problem, student debt remember?)
	
	The ''reward" for all this pain was that his family -- maybe his little sister -- wouldn't inherit all of the burden of his fantastically-expensive education. Maybe they could maintain their halfway decent Two in a lower-crime neighborhood. And if his life was going to suck anyhow, it might as well suck with access to some decent Mexican food without having to hear about it from a carefully-coiffured fake-smiling middle manager.
	
	Aiden tapped through a series of screens on his phone, carefully entering the account number the Russian had given him. \texttt{Transaction successful - thank you!} was the response. No going back now.
	
	\vspace{0.5cm}
	\hrule
	\vspace{0.5cm}
	
	``You wanted to see me?"
	
	``Ah, Aiden. Please have a seat."
	
	Aiden sat down in the deliberately-uncomfortable chair in Brannen Tragen’s office. Aiden thought often about how he would describe Brannen to his family, or to Chandler. Aiden's grandpa used to say things like, "That guy really has a punchable face." That said everything that needed to be said, really. The kind of person who makes you laugh when they get socked in a sensitive area by a little kid with a Wiffle bat in a Youtube video. Brannen Tragen was well-loved by the senior management at CMS. You'd love him too if you had power, since he would never challenge or disagree with anything you ever said.
	
	\afterpage{%
		\vspace*{\fill}
		
		\begin{tikzpicture}[remember picture, overlay]
		\draw[line width = 1pt] ($(current page.north west) + (1in,-1in)$) rectangle ($(current page.south east) + (-1in,1in)$);
		\end{tikzpicture}
		
		\begin{code}	
		\noindent To: Data Analytics Team\\
		From: Tragen, Brannen\\
		Date: March 23, 2060\\
		CC: \\
		Subject: Team Health Goals \\
		
		\noindent Good Morning Team,
		
		\noindent I just wanted to remind you that the cutoff for you \\
		to share in the responsibility to meet the team's \\ 
		health goal is next week. Please make sure that you \\
		have turned in any supporting documentation and \\ 
		supplemental justifications to accompany your HIXBOT \\
		scans before then.
		
		\vspace{0.5cm}
		
		\noindent Thank you to all who have helped us meet our first \\ quarter goals! Your efforts have been noticed and \\
		are appreciated!
		
		\vspace{0.5cm}
		
		\noindent Regards, \\
		Brannen H. Tragen, Director \\
		Office of Enterprise Data and Analytics \\
		Centers for Medicare and Medicaid Services \\
		United States Department of Health and Human Services \\
		\end{code}
		
		\vspace*{\fill}
		\clearpage
	}
	
	Brannen was, of course, impeccably dressed and his hair perfect, despite it being 8:00pm on a Friday night. His hands were folded over each other impeccably, and his pen was placed impeccably next to his impeccable pleather notepad thingy. A real corporate jerk would be carrying a tablet computer or maybe one of those Oculus holograph thingys but this was the United States Government, leading by example and cutting costs. ``I'd like to talk to you a bit about our team’s health goal."
	
	There was one in every bureau. Aiden generally got along with his coworkers. They were trying to do right by as many people as they could. Aiden's bureau was mainly responsible for collecting, cleaning, and analyzing the vast amount of biometric data coming in from the nanobots everyone was injected with starting back in 2027 and at birth thereafter. Aiden's grandpa was something called an ``actuary'' back in the day that used to do something similar, using stone tablets or 
	those vintage computers that took up three square feet on your desk and had all these ugly wires coming out everywhere.
	
	Aiden was one of the data jockeys that processed and cleaned the data to let the next-generation AIs have at it, trying to find answers. The United States had lagged behind other first-world nations for decades in the area of population health. Life expectancies had been starting to decline recently, as had live birth rates.  
	
\end{document}